First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-29 ms.tex
Another attempt at the residual flux density cut description

Our final data cut was made when inspecting the residual continuum images output from 
FHD. We test for residual flux density at source locations by calculating a fractional residual flux density RMS 
in the following way. For each snapshot 
continuum image, we find the residual flux density of all sources greater than 0.5 Jy 
subtracted within half-beam power by integrating the brightness within the source pixel.
We then scale by the integrated flux density of the sources, giving us a list of fractional
residual flux densities for the snapshot, which we then use to calculate an RMS. We found
that most snapshots had residual flux density RMS $<10\%$ with some outliers,
which we cut from the data. This cut largely overlapped with previous cuts, but removed an 
additional 95 observations. The cause of the high residual flux density RMS is yet unknown and is 
not localized by observation day, LST, pointing, or any other jackknife we have performed.

>>>>

Our final data cut was made when inspecting the snapshot residual continuum images output from 
FHD. 
We estimate a proxy for the residual flux density from foreground sources by calculating
the RMS of the fractional residual flux densities for all subtracted sources greater than
0.5 Jy within half-beam power. The fractional residual flux density is measured as the ratio
of the residual image pixel value (Jy) at the source position to the integrated flux density
of the source.
We found
that most snapshots had residual flux density RMS $<10\%$ with some outliers,
which we cut from the data. This cut largely overlapped with previous cuts, but removed an 
additional 95 observations. The cause of the high residual flux density RMS is yet unknown and is 
not localized by observation day, LST, pointing, or any other jackknife we have performed.
